Toxic code snippets on Stack Overflow

### 2017-10-23 cloverflow-tse/cloverflow.tex
Fixed the new FIXME (version to send to Nassim).

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two persons in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared. 
%and 607 (26\%)
%conflicts were discussed and resolved. 
There were 338 (15\%) conflicts between 
true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC) \FIXME{How have
  they been resolved?}. 
Another 270 pairs (12\%) were
conflicts in the classification of
the true clone pairs. Among these pairs, 145 conflicts were caused by
one investigator being more careful than the other and able to find evidence of 
copying while the other could not. Resolving the conflicts lead to a better classification,
 i.e.~from UD to QS or EX.
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.

>>>>

\textbf{Manual investigation:} 
To mitigate the human error, we deployed two persons in the manual clone
investigation process. The first author, who is a research student working on
clone detection research for three years, and the third author, who is a
software engineering research student and familiar with code clones, took the
role of the investigators performing a manual validation and classification of
the merged clone pairs. The two investigators separately went through each clone
pair candidate, looked at the clones, and decided if they are a true positive or
a false positive and classified them into an appropriate pattern. After the
validation, the results from the two investigators were compared. 
%and 607 (26\%)
%conflicts were discussed and resolved. 
There were 338 (15\%) conflicts between 
true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC).
The investigators looked at each conflicting pair together and
discussed until a consensus was made. 
Another 270 pairs (12\%) were
conflicts in the classification of
the true clone pairs. Among these pairs, 145 conflicts were caused by
one investigator being more careful than the other and being able to find evidence of 
copying while the other could not. Thus, resolving the conflicts lead to a better classification,
 i.e.~from UD to QS or EX.
%There were three conflicts where the two
%investigators could not find a consensus and the third author was involved for
%the final judgement.
